\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

% Custom colors
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{secondary}{HTML}{6c757d}
\definecolor{highlight}{HTML}{0056b3}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\color{primary}}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% No page numbers
\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries Suzanne Thornton, PhD} \\[5pt]
    {\large\color{secondary}
    \faMapMarker\ Philadelphia, PA \hspace{0.5em} | \hspace{0.5em}
    \faEnvelope\ \href{mailto:thornton.suzy@gmail.com}{thornton.suzy@gmail.com} \hspace{0.5em} | \hspace{0.5em}
    \faPhone\ 863-370-9389 \\[5pt]
    \faGithub\ \href{https://dr-suz.github.io}{dr-suz.github.io} \hspace{0.5em} | \hspace{0.5em}
    \faLinkedin\ \href{https://www.linkedin.com/in/suzanne-thornton-0a535645/}{https://www.linkedin.com/in/suzanne-thornton-0a535645/} 
    }
\end{center}

% Professional Summary
\section*{Professional Summary} %EDIT
\begin{itemize}[leftmargin=*,nosep]
    \item PhD Statistician with 5+ years of research leadership transitioning to \textbf{data science/biostatistics}
    \item Expertise in \textbf{Bayesian modeling} (hierarchical, meta-analysis), \textbf{machine learning} (Python/R), and \textbf{ethical data practices}
    \item Proven track record in \textbf{translating statistical theory} to applied solutions (NIST, clinical neurology)
    \item Earned \textbf{Google Data Analytics Certificate} on Coursera in May 2025
%    \item Strong communicator with 6+ peer-reviewed publications and \$200K+ in secured research funding
\end{itemize}

% Technical Skills
\section*{Skills and Expertise}
\begin{tabular}{@{}ll@{}}
    \textbf{Languages:} & Python (NumPy, Pandas), R (tidyverse, glmm, mclust), SQL, Stan \\
    \textbf{Tools:} & Git, LaTeX, RMarkdown, Tableau, VS Code \\
    \textbf{Methods:} & Bayesian Inference, MCMC, GLM, Bootstrapping, AUC Optimization, Measurement Error Models \\
    \textbf{Domains:} & Metrology, Clinical Predictive Analytics, Statistics and Data Science Education  
\end{tabular}

% Professional Experience
\section*{Professional Experience}
\textbf{PREP Research Scientist} \hfill 2024--Present \\ %EDIT
\textit{National Institute of Standards and Technology (NIST) | George Washington University}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
    \item Developed \textbf{Bayesian measurement error models} improving accuracy for national standards applications 
    \item Led theoretical framework for \textbf{generative AI detection} in scientific text (Python implementation) 
    \item Co-authored 2 successful grant proposals (\$144K awarded) for statistical metrology research
\end{itemize}

\noindent\textbf{Visiting Assistant/Assistant Professor of Statistics} \hfill 2019--2023 \\
\textit{Swarthmore College}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
    \item Taught mathematical statistics and implemented \textbf{ethics modules} in data science curriculum
    \item Mentored undergraduate students in \textbf{interdisciplinary research} projects %EDIT 
\end{itemize}

\noindent\textbf{Part-time Statistical Consultant} \hfill 2016--2019 \\
\textit{Rutgers Office of Statistical Consulting}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
    \item Provide clients with \textbf{experimental design}, data analysis, and interpretation of statistical results
    \item Offer methodological guidance on statistical techniques such as \textbf{regression, ANOVA, and survey methods}
    \item Provide software support and help users implement analyses in \textbf{R, SAS, and SPSS}
\end{itemize}

% Education
\vspace{-1mm}
\section*{Education}
\textbf{PhD in Statistics} \hfill 2019 \\
\textit{Rutgers University} \\
Thesis: \textit{Advanced Computing Methods for Statistical Inference} \\

\noindent\textbf{BS in Mathematics \& Statistics} \hfill 2014 \\
\textit{University of Florida}, \textit{Summa Cum Laude} 
%Thesis: \textit{Geometric ergodicity of Gibbs sampler for a hierarchical random effects model: Re-explained} 

% Select Publications
\vspace{-1mm}
\section*{Select Publications}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
    \item \textbf{Thornton S.}, et al. (2025). Semi-parametric Bayesian Measurement Error Model for Nanoparticles. \textit{(in proceedings)}
    \item \textbf{Thornton S.}, et al. (2023). Approximate Confidence Distribution Computing. \textit{NE J Stats in Data Science}
    \item \textbf{Thornton S.}, Xie M. (2023). Parameter Duality in Inference. \textit{Philosophy of Science}
    \item Choi H., \textbf{Thornton S.}, et al. (2020). Predictive Model for Drug-Resistant Epilepsy. \textit{Neurology}
    \item Michael H., \textbf{Thornton S.}, et al. (2019). Exact inference for meta-analyses. \textit{Biometrics}
\end{itemize}

%% Leadership
%\section*{Leadership \& Service}
%\textbf{Chair}, ASA LGBTQ+ Advocacy Committee (2024) \\
%\textbf{Peer Reviewer}, for $3+$ journals \\
%\textbf{National Advisory Committee}, U.S. Census Bureau (2022--2023)

\end{document}