
\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{casual}                           
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Suzanne}{Thornton}
%\title{Rutgers University}                               % optional, remove / comment the line if not wanted
\address{Philadelphia, PA}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(863)~370~9389}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{thornton.suzy@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{dr-suz.github.io/}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	
	\recipient{Pirate Ship}{}
	\date{\today}
	\opening{To the captain and the crew, \vspace{2mm}}
	\closing{\vspace{5mm} Fair winds and followin' seas,}
	\makelettertitle

I am writing to express my interest in joining your crew as a Senior Data Buccaneer. To account for the likely possibility that my professional experience is rather different from other applicants, I'll get straight to the point before elaborating further. I believe I meet the requirements for this position since (1) I have begun to experiment with Tableau and to learn SQL in my free time, (2) I have been coding in Python for the past year or so, and (3) with a broad interpretation of ``reporting and analytics", I have at least 10 years of applicable experience. Finally, I have traveled the globe to attend and present in statistics conferences and look forward to additional professional travel experiences. 

%My journey thus far has landed me in the position of a skilled statistical theorist and programmer. 

As a professional statistical researcher, I have conducted data analysis (including visualizations) primarily in the R language. More recently, as an affiliate of the National Institute for Standards and Technology (NIST), I have begun to use Python and the common data analysis packages Numpy, Pandas, and Matplotlib as it is the language of preference for my scientific collaborators. While my professional tasks have not yet required the use of relational database languages, upon realizing my desire to chart a new professional course I have become familiar with SQL independently. I am confident in my ability to implement basic data wrangling with this language and that my skill level will increase rapidly with use. Similarly, although I have historically built my own data graphics from scratch, I have started to familiarize myself with the popular data visualization tool Tableau to prepare for my new professional path. My experimentation with this software can be viewed on my public profile at the following link: https://public.tableau.com/app/profile/suzanne.thornton/vizzes. 

With a strong background in statistical research and statistical applications for scientific research, I have strong experience in the tasks of ``reporting" and ``analytics", albeit not within a business environment. My reporting experience includes academic publications from topics as varied as drug-resistant epilepsy to the philosophy of science. Indeed, research reports are my area of expertise. However, as an interdisciplinary collaborator, I am also used to providing progress reports and explanatory reports to team members from non-statistical backgrounds. My experience with data analytics is primarily oriented around descriptive and predictive purposes. I have built statistical models to describe complex physical phenomena and to predict future outcomes from observational data. Furthermore, as an instructor of statistics, I have assisted students working on semesterly projects that involved data collection and cleaning and data mining. While I have enjoyed the my time exploring the vast field of statistical research, I am ready for my next journey. I am excited about the opportunity to apply my skills to support real-world decision making. 

In addition to my technical expertise, I bring strong leadership and teamwork skills. My work at NIST has earned me two "Building the Future" grants for projects related to deepfake detection and statistical methods in clock metrology. I was also honored to be nominated by the American Statistical Association (ASA) for the National Advisory Committee to the US Census and to be selected by the ASA president to lead a working group on LGBTQ+ inclusion within the field. My leadership philosophy prioritizes fostering inclusive, collaborative environments where diverse perspectives can thrive. These qualities make me a valuable asset to any crew.

I am excited about the possibility of contributing to the creative atmosphere at the Pirate Ship while working to deliver optimal shipping solutions to small businesses. I look forward to the opportunity to discuss how my background and skills align with your needs. 
	
	\vspace{2mm}
	
	\makeletterclosing
	
\end{document}