
\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{casual}                           
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Suzanne}{Thornton}
%\title{Rutgers University}                               % optional, remove / comment the line if not wanted
\address{Philadelphia, PA}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(863)~370~9389}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{thornton.suzy@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{dr-suz.github.io/}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	
	\recipient{Community Behavioral Health}{Data Analytics' Data Warehouse}
	\date{\today }
	\opening{To whom it may concern,}
	\closing{Sincerely,}
	\makelettertitle

I am writing to express my interest in the Sr. Data Analyst position (2328). With a strong background in statistical analysis and programming, I am excited about the opportunity to apply my skills to support the accountable, high-quality delivery of health and mental wellness services. Over the past year, I have worked as an affiliate with the National Institute for Standards of Technology (NIST), where I collaborated with the Statistical Engineering Division on high-precision data analysis. This experience has deepened my expertise in managing large datasets, conducting statistical analyses, and applying data science to real-world challenges.

My passion for public health applications began during my graduate studies when I worked with a physician from Robert Wood Johnson Hospital to develop a predictive model for drug-resistant epilepsy. As the sole statistician on the project, I handled all aspects of data cleaning, model development, and evaluation, leading to a publication in \emph{Neurology}. This experience solidified my interest in using statistical tools to address pressing medical issues, a commitment I have carried forward in my career.

At NIST, I am currently developing a Bayesian measurement error model to more accurately assess the relationship between nanoparticle size and loading, and collaborating with an interdisciplinary team on guidelines for analyzing atomic clock data. These experiences have sharpened my skills in complex statistical modeling and data analysis.

In addition to my technical expertise, I bring strong leadership and teamwork skills. My work at NIST has earned me two "Building the Future" grants for projects related to deepfake detection and statistical methods in clock metrology. I was also honored to be nominated by the American Statistical Association for the National Advisory Committee to the US Census and to be selected by the ASA president to lead a working group on LGBTQ+ inclusion within the field. My leadership philosophy prioritizes fostering inclusive, collaborative environments where diverse perspectives can thrive. These qualities make me well-suited for the dynamic professional environment at CBH.

I am excited about the possibility of contributing the high quality services provided by CBH. I have provided the names and phone numbers of two references who can attest to my qualifications for this position: Dr. Adam Pintar who is currently my supervisor at NIST and Dr. Rochelle Tractenberg who is a collaborator and colleague of mine at the Collaborative for Research on Outcomes and -Metrics. My technical expertise, combined with my passion for interdisciplinary collaboration, positions me well to contribute meaningfully to your team. I look forward to the opportunity to discuss how my background and skills align with the needs of this position.

Thank you for your time and consideration.\\
	
	\vspace{2mm}
	
	\makeletterclosing
	
\end{document}


Sr. Data Analyst
Data Informatics
Clerical
Philadelphia, PA, US
Salary Range
75600.00 To 83800.00 (USD) Annually
Pending Submission
26 days ago
Requisition ID: 2328
Last Updated: 03/23/2025
Job Details
CBH is a dynamic organization dedicated to providing access to high-quality, accountable care to improve the health and mental wellness of our members. As part of our growth, we are seeking a detail-oriented Sr. Data Analyst to join our team. CBH offers a robust compensation and benefits package, including:
 

Family Planning, Fertility, Adoption Benefits
403B Retirement Plan
PTO Days/Sick Days
Wellness Program
Employee Assistance Program
Health, Dental, Vision Insurance
Medical, Prescription Drug Insurance
Tuition Reimbursement
Commuter Benefits
Flexible Spending
The Sr. Data Analyst plays a key role on the Data Analytics? Data Warehouse team to define requirements, understand business needs and workflows, and work with various business units to provide Data Analysis, Reporting, Business Intelligence (BI) and Database Backend solutions as needed by the organization.  

Core Expectations:

Community Behavioral Health (CBH) will hold each employee accountable for the following expectations which align with our mission, vision, and corporate code of conduct. 
Perform key responsibilities as detailed in this job description in a dependable, responsible, and positive manner, consistent with all state and federal guidelines.
Serve as a role model by exemplifying professional behavior, language, skills, and attire in order to promptly and accurately serve the needs of stakeholders, members and their families.
Assure adherence to CBH policies and procedures so that all work is of the highest quality and delivered in the most culturally competent and cost-effective manner.
Promote and manage diversity and acceptance within CBH and with all members and stakeholders by honoring and respecting their individuality, dignity and rights.
Offer suggestions and develop solutions to help promote effective and efficient work processes and innovative programs.
Actively participate in required meetings and complete all mandatory trainings.
Maintain high levels of advocacy and member confidentiality to ensure the success of CBH and our mission.
Assist in assuring both internal and external program integrity by being alert to and reporting suspected instances of provider and employee fraud, waste or abuse.
Evaluate/learn tools to help inform which tools best suit solutions. 
Essential Functions: 

Collaborate with stakeholders to understand, define, and document business questions needs (metrics, dimensions, charts, and dashboards).
Create and collect feedback on data visualizations (reports/dashboards) to bring insight and answers to business problems/KPIs.
Serve as primary report writer for all business units.
Responsible for recurring monthly, weekly, daily, and ad hoc reporting needs.
Collect and interpret data from multiple sources, both internal & external.
Develop, create, analyze and distribute management reports as required.
Position Requirements:

Education: Bachelor?s degree in business, computer science, statistics, mathematics or related field. 
Relevant Work Experience: Minimum of 5 years of experience as a reporting or data analyst, report writer or similar role with a strong understanding of SQL and data modeling.
5+ years of experience with ETL/ELT development, Data Modeling, Data Warehousing and SSAS preferred
5+ years of experience with contemporary data visualization technology (i.e.: Power BI.) preferred
5+ years of experience with Excel preferred
Healthcare experience is preferred
Skills:

Extract data and create reports using tools such as SQL, SSIS, SSRS, Excel, or Access
Ability to tell stories using data & visualizations
Plan, design and build ETL/ELT solutions for the Data Warehouse in a SQL Server environment 
Knowledge of modern trends, tools and approaches to collection, reporting and visualization 
Excellent written and oral communication skills 
Strong interpersonal skills with a customer service orientation 
Ability to communicate effectively between subject matter experts (SME) and developers to ensure accurate translation of business needs to implementation efforts
Solid presentation skills for both technical and non-technical audiences 
Excellent training and mentoring skills
Ability to work independently and in a team environment
Ability to work under tight project deadlines
Ability to plan, schedule and organize multiple priorities and high volume of work
Work Conditions: 

Regularly requires walking, standing, stooping, bending, sitting, reaching, pushing, pulling and/or repetitive wrist/hand movements for various lengths of time throughout the day.
Ability to utilize computers and office equipment to complete daily work responsibilities.
Requires continuous, normal hearing and vision.
Regularly works inside in areas that are adequately lighted and ventilated.  Some fluctuation in temperature. No protective equipment is routinely needed.
Must be able to adapt to continuous changes/demands of the job.