\documentclass[12pt]{letter}
\usepackage[a4paper,margin=1in]{geometry}
\begin{document}

\begin{letter}{}

\address{\parbox[t]{\textwidth}{
Hiring Manager\\
Philadelphia Department of Public Health\\
1101 Market St.13th Floor\\
Philadelphia, PA}}

\opening{Dear Hiring Manager,}

I am excited to apply for the Senior Data and Epidemiology Analyst position with the Philadelphia Department of Public Health (PDPH) and the Department of Behavioral Health and Intellectual disAbility Services (DBHIDS). With a strong background in statistical research, data analysis, and public health methodology, I am eager to contribute my expertise to support Philadelphia's efforts in addressing substance use disorders through evidence-based data initiatives.

My experience as a Research Scientist at the National Institute of Standards and Technology has provided me with expertise in Bayesian measurement error models, time series imputation, and generative AI detection, equipping me with the analytical skills necessary for managing complex health datasets. Additionally, my tenure as a statistical consultant at Rutgers University has strengthened my ability to develop predictive models, conduct cross-validation analyses, and apply statistical inference methods, all of which are critical to analyzing administrative claims data and synthesizing substance-use-related datasets from diverse sources. My background in education has further honed my ability to communicate complex statistical concepts clearly and effectively, both in writing and verbally, making technical findings accessible to diverse audiences. 

Beyond technical proficiency, I have extensive experience in interdisciplinary collaboration and data communication. As a Special Government Employee on the U.S. Census Bureau's National Advisory Committee, I engaged in government statistics and survey data strategies, ensuring methodological rigor while incorporating user feedback. Another successful collaborative experience with medical practitioners from Robert Wood Johnson Hospital resulted in a \emph{Neurology} journal article. My ability to translate statistical findings into actionable insights will enable me to provide clear, data-informed recommendations to PDPH and DBHIDS leadership.

I am particularly drawn to this opportunity because of its focus on developing a substance use disorder continuum of care surveillance program. The chance to contribute my analytical expertise to an initiative that directly impacts public health policy aligns perfectly with my passion for using data-driven solutions to improve health outcomes.

I would welcome the opportunity to discuss how my skills and experience align with your team's goals. Thank you for your time and consideration. I look forward to the possibility of contributing to Philadelphia's substance use prevention and harm reduction initiatives.


\noindent Sincerely,\\ \vspace{2ex} 
\noindent Suzanne Thornton, PhD

\end{letter}

\end{document}