
\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{casual}                           
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Suzanne}{Thornton}
%\title{Rutgers University}                               % optional, remove / comment the line if not wanted
\address{110 Frelinghuysen Road}{Piscataway, NJ}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(863)~370~9389}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{suzanne.thornton@rutgers.edu}                               % optional, remove / comment the line if not wanted
\homepage{thestatsmeow.wordpress.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	
	\recipient{Department \\
		Business}
	{Location, PA, 19191}
	\date{\today }
	\opening{Dear XXXXXX,}
	\closing{Sincerely,}
	\makelettertitle
	
	%	imba@montclair.edu
	
	
	
	
	My name is Suzanne Thornton. I am currently working at Swarthmore College as an assistant professor of statistics but I am interested in changing my career to a profession of practice. I am writing to apply for the XXXX position at XXXX.\\ \vspace{.5cm}
	% joint position of assistant professor with the Cognitive and Statistical Sciences to begin in July 2019.\\ \vspace{1cm} 
	
	Though the submission of my application is occurring before I have begun my duties at Swarthmore, as a doctoral student, my work focused on statistical computing methods driven by complex, real-world data. In particular, my research explores possible connections among Bayesian and frequentist methods through the development of new computational tools for inference. The quality of my research has been recognized though several student paper awards. Three years of applied experience as a part-time statistical consultant have also provided me with experience collaborating with scientists from other disciplines. These collaborations ultimately resulted in publications and an applied project that will be included in my doctoral thesis. Academic service has also been an important part of my training. I have served as a student mentor through a research program for undergraduate students at the Center for Discrete Mathematics and Theoretical Computer Science at Rutgers. As a graduate student, I have also taught introductory regression courses at both the undergraduate and graduate levels. I am also particularly passionate about advancing women and other minorities in the mathematical and statistical sciences. This year, some collaborators and I published a couple of articles in Significance magazine where we advocate for visible allyship with LGBT+ individuals in statistics and data science.
	%  Earlier this year, I organized a conference panel session to advocate for the visibility of LGBTQ people in statistics and data science, an effort which is being continued in the form of a prepared publication and future conference sessions in 2019.\\
	\vspace{.5cm} 
	
	Short paragraph explaining my timeline and expectations. 
	
	\vspace{.5cm} 
	
	I am excited about the opportunity to work at XXXXX. I expect to thrive personally and professionally in the position of XXXXX. Please let me know if you have any additional questions for me and feel free to view my professional website for additional information as well. Thank you for your time and consideration. \\
	
	\vspace{2cm}
	
	\makeletterclosing
	
\end{document}



Over the past four years, I have been teaching college-level statistics at an elite private college in PA. 
%While I remain passionate about fostering statistical and data literacy, 
I am passionate about data literacy and statistical literacy and wish to lead by example among communications with stakeholders and policy/decision-makers.  
I find myself eager to switch careers to a profession of practice. 
I have a strong background in statistical theory, some experience with an assortment of consulting activities, and I wish to improve my computing and programming abilities.   
I am curious about the intricacies of applied statistics, especially within the context of public service or health oriented. 






Terms 
- deep, data-driven insights
- inform strategy
- adaptability across a wide group of stakeholder
- shape and impact outcomes 
-  inclusive work environment 
- collaborate on a wide array of problems 
- results of your work will influence 
- expertise in quantitative modeling, experimentation and algorithms 
- scientific rigor and statistical methods 
- developing comprehensive knowledge 
- work cross-functionally 
- provide insights
- clearly communicate methods and conclusions
- work effectively on a team as well as a self-driven individual
- provide expertise in analyzing and visualizing large, complex, and unique data sets. 
- design and implement programs 
- create analytic datasets that combine data from multiple sources.
- clean datasets
- prepare presentations
- creating reusable code and data pipelines
- manage small to medium sized projects 

- demonstrated expertise in behavioral and/or health services research.

professional consulting; research, evaluation, and data analytics; technical assistance and training; and virtual solutions, publications, and events.

 commitment to diversity, equity, and inclusion

