\documentclass[margin,line]{res}

\usepackage{xcolor}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Suzanne M. Thornton \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
500 College Ave    & {\it Voice:}  (610) 690-6857 \\            
Department of Mathematics \& Statistics  & {\it E-mail:}  sthornt1@swarthmore.edu\\  
Swarthmore College & http://www.swarthmore.edu/suzanne-thornton\\         
Swarthmore, PA  19081 USA  &     
\end{tabular}

\vspace*{-.1in}
%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Research Interests}
Statistical computing, foundations of statistical inference, ethical statistical practice, science communication. 

%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Education}
{\bf Rutgers, The State University of New Jersey}, Piscataway, New Jersey USA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Statistics, October 2019
\item[] Thesis: Advanced computing methods for statistical inference  
%\begin{list2}
\vspace*{.05in}
%\item Current research: Approximate confidence distribution computing and a real data application.
%\item Current research: An exact approach for inference in meta-analysis with a small number of studies
%\item Advisor:  Minge Xie
%\end{list2}
\end{list1}

\vspace*{-.1in}
{\bf University of Florida} \textit{Suma Cum Laude}, Gainesville, Florida USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Statistics,  May, 2014
\item[] B.S., Mathematics, May, 2014
\end{list1}

%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Peer reviewed publications} 
{\it Approximate confidence distribution computing.} \hfill (2022)\\
{\bf Thornton} Suzanne, Wentao Li, and Minge Xie. {\em N Engl J Stat Data Sci.} (submitted) 
\vspace*{-2.5mm}

Bridging Bayesian, frequentist and fiducial inferences using confidence distribution. \hfill (2022+)\\
{\bf Thornton}, Suzanne. and Xie, Minge. In {\it Handbook on Bayesian, Fiducial and Frequentist (BFF) Inferences}. (co-editors: Berger, J.O., Meng, X.L., Reid, N. \& Xie, M.)  Chapman \& Hall, New York. (forthcoming) 
\vspace*{-2.5mm}

\textit{\small Development and validation of a predictive model of drug-resistant genetic generalized epilepsy.}\hfill(2020)\\
Hyunmi Choi, MD, MS, Kamil Detyniecki, MD, Carl Bazil, MD, PhD, Suzanne {\bf Thornton}, PhD, {\em et mult. al.}
%Peter Crosta, Hatem Tolba, MD, Lawrence J. Hirsch, MD, Erin L. Heinzen, PhD, Arjune Sen, MD, PhD, Chantal Depondt, MD, PhD, Piero Perucca, MD, PhD on behalf of The EPIGEN consortium, Gary A. Heiman, PhD. 
{\em Neurology.} %\hfill (2020)
\vspace*{-2.5mm}

\textit{Exact Inference on the Random-Effects Model for Meta-Analysis with Few Studies.}\hfill(2019)\\
Haben Michael, Suzanne {\bf Thornton}, Minge Xie, and Lu Tian. {\em Biometrics.}
\vspace*{-2.5mm}


\section{\sc Publications}  
\textit{The JEDI Corner} \hfill (June 2022)\\
{\bf Thornton}, Suzanne. {\em AMSTAT News}. 
\vspace*{-2.5mm}

\textit{Towards best practices for collecting gender and sex data.} \hfill (Feb 2022)\\
{\bf Thornton} Suzanne, Dooti Roy, Stephen Parry, Donna LaLonde, Wendy Martinez, Renee Ellis, David Corliss. {\em Significance Magazine}. 
\vspace*{-2.5mm}

\textit{Friends and allies: LGBT+ inclusion in statistics and data science.}\hfill (June 2019)\\
{\bf Thornton} Suzanne, Brittany Green, and Emma Benn. {\em Significance Magazine}. 
\vspace*{-2.5mm}

\textit{LGBT+ resources for statisticians and data scientists.}\hfill (May 2019)\\
LaLonde Donna, Wendy Martinez, Jack Miller, Miles Ott, and Suzanne {\bf Thornton}. {\em Significance Magazine Online}. 
%\vspace*{-2.5mm}
%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Honors and Awards (selected)} 
Spencer Large Research Grant\footnotemark{} (applied) 2022 
\vspace*{-2.5mm}

Dubai Cares and INEE E-Cubed Grant\footnotemark[\value{footnote}] (applied) 2021
\vspace*{-2.5mm}

Engaged Scholarship Research Grant, 2022 
\vspace*{-2.5mm}

Nominated for National Advisory Committee on Racial, Ethnic, and Other Populations (U.S. Census Bureau), 2022  

Engaged Scholarship Teaching Grant, 2021
\vspace*{-2.5mm}

Rutgers Presidential Fellowship, 2015-2019
\vspace*{-2.5mm}

ICSA Student Paper Winner, 2018
\vspace*{-2.5mm}

Rutgers Professional Development Fund, 2017 \& 2018
\vspace*{-2.5mm}

NESS Student Paper Winner, April 2017
\vspace*{-2.5mm}

Deming Scholar Award, 2016
\vspace*{-2.5mm}

Rutgers Excellence Fellowship, 2015 

\footnotetext{Interdisciplinary research with Prof. Amy Kapit of Peace and Conflict Studies.}

%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Presentations (selected)} 

Topic Contributed Speaker. Sex and gender: Data quality and ethical considerations for statisical analyses. Joint Statistical Meeting. Washington, D.C. August 2022 

Invited panelist. Facing Organizational and Ethical Considerations Resulting from COVID-19. Conference on Statistical Practice. Virtual, February 2021 

Topic contributed panelist. Balderdash, Codswallop, and Malarkey. Joint Statistical Meeting. Virtual, August 2020.

Invited speaker. Statistical computing with confidence distributions. Villanova University, Villanova, PA, December, 2019.

Invited speaker. Statistical computing with confidence distributions. Icahn School of Medicine at Mount Sinai, New York City, NY, April, 2019.

Topic contributed panelist \& organizer. Conference Within a Conference: A Forum for Sharing a Research and Education Agenda. Women in Statistics and Data Science Conference. Bellevue, WA, October, 2019.

Topic contributed panelist \& organizer. Changing the Statistics Community: Effective Strategies for Promoting an Inclusive and Equitable Culture for Women. Joint Statistical Meeting. Denver, CO, August, 2019.

Topic contributed panelist \& organizer. Preparing for Increased Gender Diversity and Inclusion in Statistics and Data Science: Important Perspectives from Gender Non-Conforming and LGBTQ Scholars. Women in Statistics and Data Science Conference. La Jolla, CA, October, 2018.

%Poster presentation. Approximate Confidence Distribution Computing.  Women in Statistics and Data Science Conference, La Jolla, CA, October, 2017.  

Session speaker. Approximate Confidence Distribution Computing.  Joint Conference on Biometrics \& Biopharmaceutical Statistics, Vienna, Austria, September, 2017.   

%Invited poster presentation. Approximate Confidence Distribution Computing.  Joint Statistical Meeting, Baltimore, MD, July, 2017. 

%Session speaker. Approximate Confidence Distribution Computing.  First International Conference on Econometrics and Statistics, Hong Kong, June, 2017.

%Session speaker. Approximate Confidence Distribution Computing.  International Chinese Statistical Association Conference, Shanghai, China, December, 2016. 

Invited poster. Introducing Approximate Confidence Distribution Computing.  72nd Annual Deming Conference on Applied Statistics, Atlantic City, NJ, December, 2016. 

Invited speaker. Introduction to Common Statistical Methods. Rutgers Center for Cell Biology and Neuroscience Weekly Seminar, Piscataway, NJ, 2016.

%Poster presentation. Approximate Confidence Distribution Computing. Workshop on Higher-Order Asymptotics and Post Selection Inference, St. Louis, MI, 2016. 

%Speed talk and poster presentation. Approximate Confidence Distribution Computing. Women in Statistics and Data Science Conference, Charlotte, NC, 2016.

Poster presentation. Approximate Confidence Distribution Computing. Third Annual Bayesian, Frequentist, Fiducial Workshop, Piscataway, NJ, 2016.  


%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Educational Experience}
\vspace{-.3cm}
\subsection{Teaching}
\vspace{-.7cm}
{\it Developed and evaluated coursework, delivered lessons, and mentored students.}
\vspace*{1mm}
\begin{list1}
\item[] {\bf Statistical Methods I} \hfill (S'20, F'21)\\
Swarthmore College
\vspace*{2mm}
\item[] {\bf Strengthening Conceptual Understanding in Introductory Statistics Courses}\\
DANA Center at University of Texas Austin \hfill(S'21, S'22)
\vspace*{2mm}
\item[] {\bf Statistical Methods II} \hfill (F'20, F'19, S'21, S'22)\\
Swarthmore College
\vspace*{2mm}
\item[] {\bf Regression Analysis} (combined graduate/undergraduate) \hfill (F'17, S'15)\\
Rutgers University
\end{list1}

\vspace*{-0.7cm}
\subsection{Undergraduate Research and Advising} 
\begin{list1}
\item[] {\em Shikha Shrestra}\hfill Summer 2020\\
\vspace*{2mm}
\item[] {\em Harron Mwangangi Kalii}\hfill 2021-2022\\
Education in Conflict Grant Proposal preparation 
\vspace*{2mm}
\item[] {\em Nancy Vu}\hfill 2021-2022\\
Education in Conflict Grant Proposal preparation 
\vspace*{2mm}
\item[] {\em Nancy Vu}\hfill Summer 2021\\
Sigma-Xi poster presentation 
\vspace*{2mm}
\item[] {\em Xoe Porterfield}\hfill Summer 2019\\
\vspace*{2mm}
\item[] {\em QSIDE Datathon4Justice}\hfill Fall 2021\\
Faculty participant 
\vspace*{2mm}
\item[] {\em Engaged Scholarship Research Grant Recipient}\hfill Summer 2021\\
The Lang Center at Swarthmore College 
\vspace*{2mm}
\item[] {\em Math/Stat minor Advisor} \hfill  2020 - 2021\\
Swarthmore College
%Summer research student Xoe Porterfield} \hfill (Summer 2020)
%REU at Rutgers}  \hfill (Summer 2018)
\end{list1}

\vspace*{-0.7cm}
\subsection{Miscellaneous}
\begin{list1}
\item[] {\em Intercultural Center Cultural Competency Workshop} \hfill 2020\\
Swarthmore College 
\vspace*{2mm}
\item[] {\em Advocating for Students of Color: There's More You Can Do} \hfill 2021\\
American Mathematical Society
\vspace*{2mm}
\item[] {\em Statistical Consultant} (part-time) \hfill 2015 - 2019\\
Rutgers University
%\vspace*{2mm}
%\item[] {\em Interdisciplinary Boot Camp in Quantitative Biology} \hfill  2015\\
%Rutgers University
%Gained hands on experience with methods for quantitative and qualitative biological research and collaborated and presented with groups of students and professors from various fields.
\end{list1}


%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Professional Service}
\vspace{-.3cm}
%{\bf Joint Statistical Meeting}\\
%{\em Session Chair} \hfill {\bf August, 2020}\\
%Served as chair of the session titled ``Data Science for the Public Good''. 
\subsection{General}
\begin{list1}
\item[] {\bf Education Council Officer} \hfill {August, 2020 - Present}\\
{\em ISOSTAT representative}
\vspace*{2mm}
 
\item[] {\bf USPROC Judge}\hfill { February 2020}\\
{\em Project evaluator} 
\vspace*{2mm}
 
\item[] {\bf International Mathematical Statistics Association} \hfill{Spring, 2021}\\
{\em Watercooler chat participant}
\vspace*{2mm}

\item[] {\bf Justice, Equity, Diversity, and Inclusion (JEDI) Organizing Group, American Statistical Association}\hfill {August, 2020 - Present}\\
{\em Communications Committee Chair} 
\vspace*{2mm}
 
\item[] {\bf Presidential initiative working group, American Statistical Association}\hfill {2020}\\
{\em Leader and organizer} 
%Lead a working group within the ASA upon request of President Wendy Martinez to support the growth of LGBTQ+ inclusion in the fields of Statistics and Data Science. The products of this group include publications, conference participation, and scholarship opportunities.
\vspace*{2mm}
\item[]{\bf LGBT+ Diversity Town Hall, Joint Statistical Meeting}\hfill{August, 2019}\\
{\em Leader and organizer.}
\end{list1}

\vspace*{-0.7cm}
\subsection{Swarthmore}
\begin{list1}
\item[] {Swatisticians Coffee Hour} \hfill {Spring 2021}
\item[] {Colloquium chair} \hfill {2021-2022}
\item[] {Hiring committee} \hfill {Spring 2020 - Present}
\item[] {Faculty advisor for Gender Minorities in Math/Stats (GeMs)} \hfill {2020-2021}
\item[] {LACOL Faculty Advisory Council} \hfill {2020 - 2022}
\item[] {Math/Stat Placement Committee}\hfill {Summer 2020}
%Worked with colleagues to develop a placement exam for Stat 021, Statistical Methods II. 
\end{list1}

\vspace*{-0.7cm}
\subsection{Rutgers}
\begin{list1}
\item[] {Graduate Student Association (GSA) Vice President} \hfill {September, 2017 - May, 2018}
%Elected officer soliciting graduate student service from university organizations and graduate students organizations; assist other GSA officers in hiring staff, planning budgets, and distributing funds. 
\item[] {University Senate, Graduate Student Representative} \hfill {September, 2016 - May, 2017}
%As an elected officer, represent graduate student interests during university senate meetings and during meetings with the Academic Standards, Regulations and Admissions Committee. 
\end{list1}

%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{\sc Professional Associations} 
\begin{list2}
\item Institute for the Quantitative Study of Inclusion, Diversity, and Equity (QSIDE)  
\item International Mathematical Statistics Association (IMS)
\item American Statistical Association (ASA)
\end{list2}

\section{\sc Computer Skills} 
\begin{list2}
\item Statistical Packages:  R (including parallel, tidyverse, RMarkdown), SAS, Minitab, SPSS
%; some experience with SAS.
\item Languages:  C++, Markdown, Python.
\item Applications:  \LaTeX, spreadsheet.
\item Operating Systems:  Mac, Windows.\\ 
\end{list2}

%\section{\sc Relevant Graduate Coursework}
%\begin{list2}
%\item Statistical learning (audit). Spring, 2017.
%\item Time series. Spring, 2017.
%\item Multivariate statistics. Fall, 2016.
%\item Stochastic optimization. Fall, 2014.
%\end{list2}



\end{resume}
\end{document}




