
\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{casual}                           
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Suzanne}{Thornton}
%\title{Rutgers University}                               % optional, remove / comment the line if not wanted
\address{500 College Ave}{Swarthmore, PA}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(863)~370~9389}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{thornton.suzy@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{dr-suz.github.io/}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	
	\recipient{National Institute of Standards PREP Program}
	{Professional Research Experience Program\\
	Statistical Engineering Division}
	\date{\today }
	\opening{Dear Hiring Committee,}
	\closing{Sincerely,}
	\makelettertitle
	

	Johns Hopkins University: Whiting School of Engineering: Commercial and Government Programs Office
	Postdoctoral Researcher (PREP0001717)
	Senior Researcher (PREP0001716)
	Senior Researcher (PREP0001720)
	
	GWU Engineering	
	PREP Research Associate - Postdoctoral Associate - ITL PREP0001718
	PREP Research Associate - Faculty (ITL) PREP0001716
	PREP Research Associate - Statistical Engineering Faculty PREP0001720
	
	My name is Suzanne Thornton. After teaching college-level statistics for the past few years, I am looking forward to orienting the next chapter of my career towards statistical practice. I have found that I am most motivated and content when I can apply statistical theory and programming to solve real-world problems. I am writing to apply for the XXXX position at XXX and to begin a career of practice where I can put my strong theoretical statistical knowledge to use.\\ \vspace{.5cm}

Since beginning my work as a statistics faculty member in 2019, my professional expertise has mainly revolved around my work as an educator and as a published statistical researcher. As an educator, I strive to make my lessons accessible and teach statistical practice as a language for understanding science that works best when it is used responsibly and ethically. All of my course content is publicly available on my personal website and I take every opportunity to communicate lessons about data and statistical literacy to audiences beyond my own classroom. As a statistical researcher, I have several technical publications involving theoretical and computational statistical developments as well as many non-technical publications on issues relevant to my discipline. I am a skilled statistical programer (mainly working with R) and have self-taught myself various data science skills (e.g. SQL, Git) in preparation for my new career path. I am experienced with grant writing and managing/mentoring small groups of people from different backgrounds and with various skillsets. %These collaborations have led to publications and the development of new statistical tools. 
I am passionate about my service to the disciplines of statistics and data science which has provided me with many leadership opportunities. This year, I organized (and will be presenting in) a Joint Statistical Meetings conference session about incorporating social justice and ethical reasoning into the undergraduate statistics curriculum. I have also served the discipline through my work at the American Statistical Association as a founding member of the Justice, Equity, Diversity, and Inclusion Organizing Group (2021) and as the appointed leader of the LGBT+ Inclusivity and Diversity Working Group (2020). In 2022, I was nominated to serve on the National Advisory committee to the US Census. I am in the second of my three year term where I work with other dedicated volunteers to make recommendations on how Census data is obtained, stored, and applied in ways that are consistent with ethical statistical practice.   
	
	
	\vspace{.5cm} 
	
	I am excited about the opportunity to begin a career at XXX. Please let me know if you have any additional questions for me and feel free to view my professional website (link below) for additional information. I am actively searching for fulfilling full-time career opportunities and I hope to begin my new job by the end of the calendar year. Thank you for your time and consideration.\\
	
	\vspace{1cm}
	
	\makeletterclosing
	
\end{document}

